Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-02-21 paper/main.tex
Added Chris contact details/acknowledgments

\author{Eric Martin \\
\texttt{eric@ericmart.in} \\
\And
Chris Cundy
Department of XX \\
University of XX \\
City, Country \\
\texttt{c.cundy@berkeley.edu} \\
}

@@

\subsubsection*{Acknowledgments}
We would like to acknowledge Kevin Bowers, Alex Meiburg, JD Co-Reyes, Carson
McNeil, Andy Palan, and several others for fruitful conversations and guidance.

>>>>

\author{Eric Martin \\
\texttt{eric@ericmart.in} \\
\And
Chris Cundy \\
Department of Computer Science\\
University of California, Berkeley\\
Berkeley, CA 94720, USA\thanks{Currently at the Future of Humanity Institute, University of Oxford, Oxford, UK} \\
\texttt{c.cundy@berkeley.edu} \\
}

@@

\subsubsection*{Acknowledgments}
We would like to acknowledge Kevin Bowers, Alex Meiburg, JD Co-Reyes, Carson
McNeil, Andy Palan, Sören Mindermann, and several others for fruitful conversations and guidance.
